\mytitle

### 2023-06-07 expanded-paper.tex
Final updates for Computer Journal

% 
% This file has been expanded from LaTeX file (paper.tex)
%   to make this straight forward LaTeX file (expanded-paper.tex)
%     that depends on nothing (it inputs no files apart from the document class files).
%       Each required file's text was input in situ - search for % expand
% 
% (Otherwise the file paper.tex would use BibTeX, a macro file, tables of contents, its own and the other files's .aux files, and includes various files in generated/*, etc.)
%

@@

\bibitem{a=b}
Petkovsek, M., Wilf, H. and Zeilberger, D. (1996) {\em {$A=B$}}, A~K~Peters.
  Ltd.
\newblock \url{www2.math.upenn.edu/}\midurl{~wilf/}\midurl{AeqB.html}

@@

\bibitem{computational-thinking}
McOwen, P.~W. and Curzon, P. (2020) {\em The Power of Computational Thinking},
  World Scientific Publishing.

@@

\bibitem{avianFluModel}
Ferguson, N.~M., Cummings, D. A.~T., Fraser, C., Cajka, J.~C., Cooley, P.~C.
  and Burke, D.~S. (2005) ``Strategies for containing an emerging influenza
  pandemic in {Southeast Asia},'' {\em Nature}, \textbf{437}:209--214.
\newblock \doi{10.1038/nature04017}

\bibitem{originalICmodel}
Ferguson, N.~M., Cummings, D. A.~T., Fraser, C., Cajka, J.~C., Cooley, P.~C.
  and Burke, D.~S. (2006) ``Strategies for mitigating an influenza pandemic,''
  {\em Nature}, \textbf{442}:448--452.
\newblock \doi{10.1038/nature04795}

@@

\bibitem{jupyter-study}
Pimentel, J.~F., Murta, L., Braganholo, V. and Freire, J. (2019) ``A
  large-scale study about quality and reproducibility of {Jupyter} notebooks,''
  {\em in 2019 IEEE/ACM 16th International Conference on Mining Software
  Repositories {(MSR)}}, pp.~507--517.
\newblock \doi{10.1109/MSR.2019.00077}

\bibitem{trisovic}
Trisovic, A., Lau, M.~K., Pasquier, T. and Crosas, M. (2022) ``A large-scale
  study on research code quality and execution nature research,'' {\em
  Scientific Data}, \textbf{9}(60).
\newblock \doi{10.1038/s41597-022-01143-6}

@@

\bibitem{data-access}
Gabelica, M., Boj{\v c}i{\' c}, R. and Puljak, L. (2020) ``Many researchers
  were not compliant with their published data sharing statement: mixed-methods
  study,'' {\em Journal of Clinical Epidemiology}.
\newblock \doi{0.1016/j.jclinepi.2022.05.019}

\bibitem{reproducible-manifesto}
Munaf{\`o}, M.~R., Nosek, B.~A., Bishop, D. V.~M., Button, K.~S., Chambers,
  C.~D., Percie~du Sert, N., Simonsohn, U., Wagenmakers, E.-J., Ware, J.~J. and
  Ioannidis, J. P.~A. (2017) ``A manifesto for reproducible science,'' {\em
  Nature Human Behaviour}, \textbf{1}(1):0021.
\newblock \doi{10.1038/s41562-016-0021}

@@

\bibitem{MMR-fraud}
Godlee, F., Smith, J. and Marcovitch, H. (2011) ``Wakefield's article linking
  {MMR} vaccine and autism was fraudulent,'' {\em BMJ}, \textbf{342}(c7452).
\newblock \doi{10.1136/bmj.c7452}

@@

\bibitem{elns}
Machina, H.~K. and Wild, D.~J. (2013) ``Electronic laboratory notebooks
  progress and challenges in implementation,'' {\em Journal of Laboratory
  Automation}, \textbf{18}(4):264--268.
\newblock \doi{0.1177/2211068213484471}

@@

\bibitem{maneage}
Akhlaghi, M., Infante-Sainz, R., Roukema, B.~F., Khellat, M., Valls-Gabaud, D.
  and Baena-Gall{\'e}, R. (May 2021) ``Toward long-term and archivable
  reproducibility,'' {\em Computing in Science {\&} Engineering},
  \textbf{23}(3):82--91.
\newblock \url{https:/}\midurl{/}\midurl{maneage.org},
  \doi{10.1109/mcse.2021.3072860}

@@

\bibitem{relit}
Thimbleby, H. and Williams, D. (2018) ``A tool for publishing reproducible
  algorithms {\&} {A} reproducible, elegant algorithm for sequential
  experiments,'' {\em Science of Computer Programming}, \textbf{156}:45--67.
\newblock \url{GitHub.com/}\midurl{haroldthimbleby/}\midurl{relit},
  \doi{10.1016/j.scico.2017.12.010}

\bibitem{notebook-patent}
Gray, T.~W. and Wolfram, S. (26 March 2013) {\em Method and system for
  presenting input expressions and evaluations of the input expressions on a
  workspace of a computational system}, US patent no{\@.} 8,407,580~B2.

\bibitem{jupyter-history}
Granger, B.~E. and P{\'e}rez, F. (2021) ``Jupyter: {Thinking} and storytelling
  with code and data,'' {\em Computing in Science {\&} Engineering},
  \textbf{23}(2):7--14.
\newblock \doi{10.1109/MCSE.2021.3059263}

@@

\bibitem{se-bias}
Friedman, B. and Nissenbaum, H. (1996) ``Bias in computer systems,'' {\em ACM
  Transactions on Information Systems}, \textbf{14}(3):330--347.
\newblock \doi{10.1145/230538.230561}

\bibitem{sas9.2}
Laurain, E., Ayav, C., Erpelding, M.-L., Kessler, M., Brian{\c{c}}on, S.,
  Brunaud, L. and Frimat, L. (2022) ``Targets for parathyroid hormone in
  secondary hyperparathyroidism: is a ``one-size-fits-all'' approach
  appropriate? {A} prospective incident cohort study,'' {\em BMC nephrology},
  \textbf{15}:132.
\newblock \doi{10.1186/1471-2369-15-132}

@@

\bibitem{assurance-case}
Habli, I., Alexander, R., Hawkins, R., Sujan, M., McDermid, J., Picardi, C. and
  Lawton, T. (2020) ``Enhancing {COVID-19} decision making by creating an
  assurance case for epidemiological models,'' {\em BMJ Health {\&} Care
  Informatics}, \textbf{27}(e100165):1--5.
\newblock \doi{10.1136/bmjhci-2020-100165}

\bibitem{assessing-quality}
Kelly, D. and Sanders, R. (2008) {\em Assessing the Quality of Scientific
  Software}, First International Workshop on Software Engineering For
  Computational Science and Engineering {(see
  \cite{assessing-quality-conference}}), Leipzig.
\newblock
  \url{citeseerx.ist.psu.edu/}\midurl{viewdoc/}\midurl{summary?doi=10.1.1.526.5076}

@@

\bibitem{tripod}
Moons, K.~G., Altman, D.~G., Reitsma, J.~B., Ioannidis, J.~P., Macaskill, P.,
  Steyerberg, E.~W., Vickers, A.~J., Ransohoff, D.~F. and Collins, G.~S. (2015)
  ``Transparent reporting of a multivariable prediction model for individual
  prognosis or diagnosis ({TRIPOD}): {Explanation} and elaboration,'' {\em
  Annals of Internal Medicine}, \textbf{162}(1):W1--73.
\newblock \doi{10.7326/M14-0698}

@@

\bibitem{forsyth}
Ahrens, J.~H. and Dieter, U. (1973) ``Extensions of {Forsythe's} method for
  random sampling from the normal distribution,'' {\em Mathematics of
  Computation}, \textbf{27}:927--937.
\newblock \doi{10.1090/S0025-5718-1973-0329190-8}

\bibitem{Normal-Distributions}
Ahrens, J.~H. and Dieter, U. (1972) ``Computer methods for sampling from the
  exponential and normal distributions,'' {\em Communications of the ACM},
  \textbf{15}(10):873--882.
\newblock \doi{10.1145/355604.361593}

@@

\bibitem{haskell}
O'Sullivan, B., Stewart, D. and Goerzen, J. (2008) {\em Real World Haskell},
  O'Reilly Media.
\newblock \url{book.realworldhaskell.org}

@@

\bibitem{codecheck}
Scheuber, A. and {van Elsland}, S.~L. (1 June 2020) {\em Codecheck confirms
  reproducibility of {COVID-19} model results}.
\newblock
  \url{www.imperial.ac.uk/}\midurl{news/}\midurl{197875/}\midurl{codecheck-}\midurl{confirms-}\midurl{reproducibility-}\midurl{covid-}\midurl{19-}\midurl{model-}\midurl{results}

@@

\bibitem{NVP}
{Hatton}, L. and {Roberts}, A. (1994) ``How accurate is scientific software?''
  {\em IEEE Transactions on Software Engineering}, \textbf{20}(10):785--797.
\newblock \doi{10.1109/32.328993}

@@

\bibitem{bad-code}
Richards, D. and Boudnik, K. (16 May 2020) ``{Neil} {Ferguson's} {Imperial}
  model could be the most devastating software mistake of all time,'' {\em The
  Telegraph}.
\newblock
  \url{www.telegraph.co.uk/}\midurl{technology/}\midurl{2020/}\midurl{05/}\midurl{16/}\midurl{neil-}\midurl{fergusons-}\midurl{imperial-}\midurl{model-}\midurl{could-}\midurl{devastating-}\midurl{software-}\midurl{mistake}

\bibitem{pseudo}
Zlojutro, A., Rey, D. and Gardner, L. (2019) ``A decision-support framework to
  optimize border control for global outbreak mitigation,'' {\em Nature
  Scientific Reports}, \textbf{9}(2216).
\newblock \doi{10.1038/s41598-019-38665-w}

@@

\bibitem{flu-model}
Sander, B., Nizam, A., {Garrison Jr}, L.~P., Postma, M.~J., Halloran, M.~E. and
  {Longini Jr}, I.~M. (2009) ``Economic evaluation of influenza pandemic
  mitigation strategies in the {US} using a stochastic microsimulation
  transmission model,'' {\em Value Health}, \textbf{12}(2):226--233.
\newblock \doi{10.1111/j.1524-4733.2008.00437.x}

@@

\bibitem{psychological-modeling}
Guest, O. and Martin, A.~E. (2021) ``How computational modeling can force
  theory building in psychological science,'' {\em Perspectives on
  Psychological Science}, \textbf{16}(4):789--802.
\newblock \doi{10.1177/1745691620970585}

@@

\bibitem{ourReview}
Ladkin, P.~B., Littlewood, B., Thimbleby, H. and Thomas, M. (2020) ``The {Law
  Commission} presumption concerning the dependability of computer evidence,''
  {\em Digital Evidence and Electronic Signature Law Review},
  \textbf{17}:1--14.
\newblock \doi{10.14296/deeslr.v17i0.5143}

@@

\bibitem{unfinished}
Kissler, S.~M., Tedijanto, C., Goldstein, E., Grad, Y.~H. and Lipsitch, M.
  (2020) ``Projecting the transmission dynamics of {SARS-CoV-2} through the
  postpandemic period,'' {\em Science}, \textbf{368}(6493):860--868.
\newblock \doi{10.1126/science.abb5793}

@@

\bibitem{preclinical-reproducibility}
Freedman, L.~P., Cockburn, I.~M. and Simcoe, T.~S. (2015) ``The economics of
  reproducibility in preclinical research,'' {\em PLOS Biology},
  \textbf{13}(6):e1002165.
\newblock \doi{10.1371/journal.pbio.1002165}

@@

\bibitem{fair-principles}
Wood-Charlson, E.~M., Crockett, Z., Erdmann, C., Arkin, A.~P. and Robinson,
  C.~B. (2022) ``Ten simple rules for getting and giving credit for data,''
  {\em PLoS Computational Biology}, \textbf{18}(9):e1010476.
\newblock \doi{10.1371/ journal.pcbi.1010476}

\bibitem{cbc}
Woodcock, J. C.~P., Larsen, P.~G., Bicarregui, J.~C. and Fitzgerald, J.~S.
  (2009) ``Formal methods: {Practice} and experience,'' {\em ACM Computing
  Surveys}, \textbf{41}(4):1--36.
\newblock \doi{10.1145/1592434.1592436}

@@

\bibitem{ABCs-SE}
Stol, K.-J. and Fitzgerald, B. (2018) ``The {ABC} of software engineering
  research,'' {\em ACM Transactions on Software Engineering and Methodology},
  \textbf{27}(3):1--51.
\newblock \doi{10.1145/3241743}

@@

\bibitem{Executable-Paper}
Gabriela, A. and Capone, R. (2011) ``Executable paper {Grand Challenge}
  workshop,'' {\em Procedia Computer Science}, \textbf{4}:577--578.
\newblock \doi{10.1016/j.procs.2011.04.060}

\bibitem{RMarkdown}
Xie, Y., Allaire, J.~J. and Grolemund, G. (2020) {\em R Markdown: The
  Definitive Guide}, Chapman {\&} Hall/CRC.

@@

\bibitem{debt}
Falessi, D. and Kruchten, P. (2015) ``Five reasons for including technical debt
  in the software engineering curriculum,'' {\em in Proceedings of the 2015
  European Conference on Software Architecture Workshops}, ECSAW'15, ACM,
  pp.~28:1--28:4.
\newblock \doi{10.1145/2797433.2797462}

@@

\bibitem{reproducibility}
Benureau, F. C.~Y. and Rougier, N.~P. (2018) ``Re-run, repeat, reproduce,
  reuse, replicate: {Transforming} code into scientific contributions,'' {\em
  Frontiers in Neuroinformatics}, \textbf{11}(69).
\newblock \doi{10.3389/fninf.2017.00069}

>>>>

% Please do not edit this file, expanded-paper.tex!
% It was generated automatically from its master file paper.tex, by programs/expand.js
% Get everything from https://github.com/haroldthimbleby/improving-science
% 
% This file expands the LaTeX file (paper.tex), which has complex dependencies,
%   to make this simple LaTeX file (expanded-paper.tex)
%     that depends on nothing, apart from its standard document class.
%       This expanded file depends on no other files, as instead
%         each required file's text was input and expanded recursively - search for '% expand' in the expanded file below.
% 
% (The original file is dependent on BibTeX (.bst and .bbl files), a macro file, table of contents,
%   its own and other files' .aux files,
%     as well as various data files in the directory generated
%       etc. All these file dependencies have been removed.)
%

@@

\bibitem{a=b}
Petkovsek, M., Wilf, H., and Zeilberger, D. (1996) {\em {$A=B$}}, A~K~Peters.
  Ltd.
\newblock \url{www2.math.upenn.edu/}\midurl{~wilf/}\midurl{AeqB.html}

@@

\bibitem{computational-thinking}
McOwen, P.~W., and Curzon, P. (2020) {\em The Power of Computational Thinking},
  World Scientific Publishing.

@@

\bibitem{avianFluModel}
Ferguson, N.~M., Cummings, D. A.~T., Fraser, C., Cajka, J.~C., Cooley, P.~C.,
  and Burke, D.~S. (2005) ``Strategies for containing an emerging influenza
  pandemic in {Southeast Asia},'' {\em Nature}, \textbf{437}:209--214.
\newblock \doi{10.1038/nature04017}

\bibitem{originalICmodel}
Ferguson, N.~M., Cummings, D. A.~T., Fraser, C., Cajka, J.~C., Cooley, P.~C.,
  and Burke, D.~S. (2006) ``Strategies for mitigating an influenza pandemic,''
  {\em Nature}, \textbf{442}:448--452.
\newblock \doi{10.1038/nature04795}

@@

\bibitem{jupyter-study}
Pimentel, J.~F., Murta, L., Braganholo, V., and Freire, J. (2019) ``A
  large-scale study about quality and reproducibility of {Jupyter} notebooks,''
  {\em in 2019 IEEE/ACM 16th International Conference on Mining Software
  Repositories {(MSR)}}, pp.~507--517.
\newblock \doi{10.1109/MSR.2019.00077}

\bibitem{trisovic}
Trisovic, A., Lau, M.~K., Pasquier, T., and Crosas, M. (2022) ``A large-scale
  study on research code quality and execution nature research,'' {\em
  Scientific Data}, \textbf{9}(60).
\newblock \doi{10.1038/s41597-022-01143-6}

@@

\bibitem{data-access}
Gabelica, M., Boj{\v c}i{\' c}, R., and Puljak, L. (2020) ``Many researchers
  were not compliant with their published data sharing statement: mixed-methods
  study,'' {\em Journal of Clinical Epidemiology}.
\newblock \doi{0.1016/j.jclinepi.2022.05.019}

\bibitem{reproducible-manifesto}
Munaf{\`o}, M.~R., Nosek, B.~A., Bishop, D. V.~M., Button, K.~S., Chambers,
  C.~D., Percie~du Sert, N., Simonsohn, U., Wagenmakers, E.-J., Ware, J.~J.,
  and Ioannidis, J. P.~A. (2017) ``A manifesto for reproducible science,'' {\em
  Nature Human Behaviour}, \textbf{1}(1):0021.
\newblock \doi{10.1038/s41562-016-0021}

@@

\bibitem{MMR-fraud}
Godlee, F., Smith, J., and Marcovitch, H. (2011) ``Wakefield's article linking
  {MMR} vaccine and autism was fraudulent,'' {\em BMJ}, \textbf{342}(c7452).
\newblock \doi{10.1136/bmj.c7452}

@@

\bibitem{elns}
Machina, H.~K., and Wild, D.~J. (2013) ``Electronic laboratory notebooks
  progress and challenges in implementation,'' {\em Journal of Laboratory
  Automation}, \textbf{18}(4):264--268.
\newblock \doi{0.1177/2211068213484471}

@@

\bibitem{maneage}
Akhlaghi, M., Infante-Sainz, R., Roukema, B.~F., Khellat, M., Valls-Gabaud, D.,
  and Baena-Gall{\'e}, R. (May 2021) ``Toward long-term and archivable
  reproducibility,'' {\em Computing in Science {\&} Engineering},
  \textbf{23}(3):82--91.
\newblock \url{https:/}\midurl{/}\midurl{maneage.org},
  \doi{10.1109/mcse.2021.3072860}

@@

\bibitem{relit}
Thimbleby, H., and Williams, D. (2018) ``A tool for publishing reproducible
  algorithms {\&} {A} reproducible, elegant algorithm for sequential
  experiments,'' {\em Science of Computer Programming}, \textbf{156}:45--67.
\newblock \url{GitHub.com/}\midurl{haroldthimbleby/}\midurl{relit},
  \doi{10.1016/j.scico.2017.12.010}

\bibitem{notebook-patent}
Gray, T.~W., and Wolfram, S. (26 March 2013) {\em Method and system for
  presenting input expressions and evaluations of the input expressions on a
  workspace of a computational system}, US patent no{\@.} 8,407,580~B2.

\bibitem{jupyter-history}
Granger, B.~E., and P{\'e}rez, F. (2021) ``Jupyter: {Thinking} and storytelling
  with code and data,'' {\em Computing in Science {\&} Engineering},
  \textbf{23}(2):7--14.
\newblock \doi{10.1109/MCSE.2021.3059263}

@@

\bibitem{se-bias}
Friedman, B., and Nissenbaum, H. (1996) ``Bias in computer systems,'' {\em ACM
  Transactions on Information Systems}, \textbf{14}(3):330--347.
\newblock \doi{10.1145/230538.230561}

\bibitem{sas9.2}
Laurain, E., Ayav, C., Erpelding, M.-L., Kessler, M., Brian{\c{c}}on, S.,
  Brunaud, L., and Frimat, L. (2022) ``Targets for parathyroid hormone in
  secondary hyperparathyroidism: is a ``one-size-fits-all'' approach
  appropriate? {A} prospective incident cohort study,'' {\em BMC nephrology},
  \textbf{15}:132.
\newblock \doi{10.1186/1471-2369-15-132}

@@

\bibitem{assurance-case}
Habli, I., Alexander, R., Hawkins, R., Sujan, M., McDermid, J., Picardi, C.,
  and Lawton, T. (2020) ``Enhancing {COVID-19} decision making by creating an
  assurance case for epidemiological models,'' {\em BMJ Health {\&} Care
  Informatics}, \textbf{27}(e100165):1--5.
\newblock \doi{10.1136/bmjhci-2020-100165}

\bibitem{assessing-quality}
Kelly, D., and Sanders, R. (2008) {\em Assessing the Quality of Scientific
  Software}, First International Workshop on Software Engineering For
  Computational Science and Engineering {(see
  \cite{assessing-quality-conference}}), Leipzig.
\newblock
  \url{citeseerx.ist.psu.edu/}\midurl{viewdoc/}\midurl{summary?doi=10.1.1.526.5076}

@@

\bibitem{tripod}
Moons, K.~G., Altman, D.~G., Reitsma, J.~B., Ioannidis, J.~P., Macaskill, P.,
  Steyerberg, E.~W., Vickers, A.~J., Ransohoff, D.~F., and Collins, G.~S.
  (2015) ``Transparent reporting of a multivariable prediction model for
  individual prognosis or diagnosis ({TRIPOD}): {Explanation} and
  elaboration,'' {\em Annals of Internal Medicine}, \textbf{162}(1):W1--73.
\newblock \doi{10.7326/M14-0698}

@@

\bibitem{forsyth}
Ahrens, J.~H., and Dieter, U. (1973) ``Extensions of {Forsythe's} method for
  random sampling from the normal distribution,'' {\em Mathematics of
  Computation}, \textbf{27}:927--937.
\newblock \doi{10.1090/S0025-5718-1973-0329190-8}

\bibitem{Normal-Distributions}
Ahrens, J.~H., and Dieter, U. (1972) ``Computer methods for sampling from the
  exponential and normal distributions,'' {\em Communications of the ACM},
  \textbf{15}(10):873--882.
\newblock \doi{10.1145/355604.361593}

@@

\bibitem{haskell}
O'Sullivan, B., Stewart, D., and Goerzen, J. (2008) {\em Real World Haskell},
  O'Reilly Media.
\newblock \url{book.realworldhaskell.org}

@@

\bibitem{codecheck}
Scheuber, A., and {van Elsland}, S.~L. (1 June 2020) {\em Codecheck confirms
  reproducibility of {COVID-19} model results}.
\newblock
  \url{www.imperial.ac.uk/}\midurl{news/}\midurl{197875/}\midurl{codecheck-}\midurl{confirms-}\midurl{reproducibility-}\midurl{covid-}\midurl{19-}\midurl{model-}\midurl{results}

@@

\bibitem{NVP}
{Hatton}, L., and {Roberts}, A. (1994) ``How accurate is scientific software?''
  {\em IEEE Transactions on Software Engineering}, \textbf{20}(10):785--797.
\newblock \doi{10.1109/32.328993}

@@

\bibitem{bad-code}
Richards, D., and Boudnik, K. (16 May 2020) ``{Neil} {Ferguson's} {Imperial}
  model could be the most devastating software mistake of all time,'' {\em The
  Telegraph}.
\newblock
  \url{www.telegraph.co.uk/}\midurl{technology/}\midurl{2020/}\midurl{05/}\midurl{16/}\midurl{neil-}\midurl{fergusons-}\midurl{imperial-}\midurl{model-}\midurl{could-}\midurl{devastating-}\midurl{software-}\midurl{mistake}

\bibitem{pseudo}
Zlojutro, A., Rey, D., and Gardner, L. (2019) ``A decision-support framework to
  optimize border control for global outbreak mitigation,'' {\em Nature
  Scientific Reports}, \textbf{9}(2216).
\newblock \doi{10.1038/s41598-019-38665-w}

@@

\bibitem{flu-model}
Sander, B., Nizam, A., {Garrison Jr}, L.~P., Postma, M.~J., Halloran, M.~E.,
  and {Longini Jr}, I.~M. (2009) ``Economic evaluation of influenza pandemic
  mitigation strategies in the {US} using a stochastic microsimulation
  transmission model,'' {\em Value Health}, \textbf{12}(2):226--233.
\newblock \doi{10.1111/j.1524-4733.2008.00437.x}

@@

\bibitem{psychological-modeling}
Guest, O., and Martin, A.~E. (2021) ``How computational modeling can force
  theory building in psychological science,'' {\em Perspectives on
  Psychological Science}, \textbf{16}(4):789--802.
\newblock \doi{10.1177/1745691620970585}

@@

\bibitem{ourReview}
Ladkin, P.~B., Littlewood, B., Thimbleby, H., and Thomas, M. (2020) ``The {Law
  Commission} presumption concerning the dependability of computer evidence,''
  {\em Digital Evidence and Electronic Signature Law Review},
  \textbf{17}:1--14.
\newblock \doi{10.14296/deeslr.v17i0.5143}

@@

\bibitem{unfinished}
Kissler, S.~M., Tedijanto, C., Goldstein, E., Grad, Y.~H., and Lipsitch, M.
  (2020) ``Projecting the transmission dynamics of {SARS-CoV-2} through the
  postpandemic period,'' {\em Science}, \textbf{368}(6493):860--868.
\newblock \doi{10.1126/science.abb5793}

@@

\bibitem{preclinical-reproducibility}
Freedman, L.~P., Cockburn, I.~M., and Simcoe, T.~S. (2015) ``The economics of
  reproducibility in preclinical research,'' {\em PLOS Biology},
  \textbf{13}(6):e1002165.
\newblock \doi{10.1371/journal.pbio.1002165}

@@

\bibitem{fair-principles}
Wood-Charlson, E.~M., Crockett, Z., Erdmann, C., Arkin, A.~P., and Robinson,
  C.~B. (2022) ``Ten simple rules for getting and giving credit for data,''
  {\em PLoS Computational Biology}, \textbf{18}(9):e1010476.
\newblock \doi{10.1371/ journal.pcbi.1010476}

\bibitem{cbc}
Woodcock, J. C.~P., Larsen, P.~G., Bicarregui, J.~C., and Fitzgerald, J.~S.
  (2009) ``Formal methods: {Practice} and experience,'' {\em ACM Computing
  Surveys}, \textbf{41}(4):1--36.
\newblock \doi{10.1145/1592434.1592436}

@@

\bibitem{ABCs-SE}
Stol, K.-J., and Fitzgerald, B. (2018) ``The {ABC} of software engineering
  research,'' {\em ACM Transactions on Software Engineering and Methodology},
  \textbf{27}(3):1--51.
\newblock \doi{10.1145/3241743}

@@

\bibitem{Executable-Paper}
Gabriela, A., and Capone, R. (2011) ``Executable paper {Grand Challenge}
  workshop,'' {\em Procedia Computer Science}, \textbf{4}:577--578.
\newblock \doi{10.1016/j.procs.2011.04.060}

\bibitem{RMarkdown}
Xie, Y., Allaire, J.~J., and Grolemund, G. (2020) {\em R Markdown: The
  Definitive Guide}, Chapman {\&} Hall/CRC.

@@

\bibitem{debt}
Falessi, D., and Kruchten, P. (2015) ``Five reasons for including technical
  debt in the software engineering curriculum,'' {\em in Proceedings of the
  2015 European Conference on Software Architecture Workshops}, ECSAW'15, ACM,
  pp.~28:1--28:4.
\newblock \doi{10.1145/2797433.2797462}

@@

\bibitem{reproducibility}
Benureau, F. C.~Y., and Rougier, N.~P. (2018) ``Re-run, repeat, reproduce,
  reuse, replicate: {Transforming} code into scientific contributions,'' {\em
  Frontiers in Neuroinformatics}, \textbf{11}(69).
\newblock \doi{10.3389/fninf.2017.00069}
